\documentclass[12pt,]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}


  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}




\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother




\setcounter{secnumdepth}{0}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs}



\title{Political Donor Motivations and Social Media: A Time-Series Analysis  }



\author{\Large \vspace{0.05in} \newline\normalsize\emph{}  }


\date{}

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\itshape}
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}





\newtheorem{hypothesis}{Hypothesis}
\usepackage{setspace}


% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{graphicx}

% move the hyperref stuff down here, after header-includes, to allow for - \usepackage{hyperref}

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \PassOptionsToPackage{hyphens}{url}\usepackage[draft,unicode=true]{hyperref}
\fi
}

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={ ()},
             pdfkeywords = {},  
            pdftitle={Political Donor Motivations and Social Media: A Time-Series Analysis},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

% Add an option for endnotes. -----


% add tightlist ----------
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% add some other packages ----------

% \usepackage{multicol}
% This should regulate where figures float
% See: https://tex.stackexchange.com/questions/2275/keeping-tables-figures-close-to-where-they-are-mentioned
\usepackage[section]{placeins}


\begin{document}
	
% \pagenumbering{arabic}% resets `page` counter to 1 
%
% \maketitle

{% \usefont{T1}{pnc}{m}{n}
\setlength{\parindent}{0pt}
\thispagestyle{plain}
{\fontsize{18}{20}\selectfont\raggedright 
\maketitle  % title \par  

}

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
\textbf{\authorfont } \hskip 15pt \emph{\small }   

}

}






\vskip -8.5pt


 % removetitleabstract

\noindent \doublespacing 

The two predominant theories of political donor motivations are the
access-oriented model and the consumption model. In the access-oriented
model, political donors contribute to campaigns in order to seek and
acquire access and influence with politicians in order to get them to
support specific policy issues. The consumption model of donors sees
political contributions as being an extension of voting along a
participatory spectrum, and that donors support candidates who they
already know support policy issues that the donors care about. This
paper combines Twitter and Facebook posts from politicians in the 2016
election cycle to measure public support of policy issues and
administrative political donation data. These two datasets are analyzed
in conjunction with one another to see if politicians' public support of
various policy issues on social media precede, lag, or have no
relationship with donations from various clusters of political donors.
The access-oriented model of political donors would predict that
donations from specific groups of donors would precede public support of
various policies. In contrast, the consumption model of political donors
would predict that donations from various groups of donors would lag in
response to public support of policy issues by candidates. This paper
sets these two models of political donors against each to see if
evidence of either model is found in observational data.

\hypertarget{data}{%
\section{Data}\label{data}}

Data for this research comes from two primary sources: politicians'
social media posts and political donation data. For social media posts,
this paper used the Facebook and Twitter APIs to collect social media
posts from all candidates for the Wisconsin State Senate and Wisconsin
State Assembly during the 2016 election cycle (\emph{n} = 82,851). A
subset of these posts were hand-coded into 27 topical categories. This
subset was used to train a BERT deep learning transfer model that was
used to predict the remainder of the posts (train dataset = 8,242, 10\%
of posts; validation dataset = 4,122, 5\% of posts). Political donation
data for all candidates to the Wisconsin State Legislature during the
2016 election cycle was collected from the Wisconsin Campaign
Information System (CFIS). These donations were used to create a network
of political donations with candidates and donors serving as nodes and
donations between them as edges. This network was clustered into
distinct communities so that donors in each community are most similar
to one another based on which campaigns they contributed to.

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

These two datasets were analyzed against each other using the granger
causality time-series methodology. This methodology detects whether
movements in one time series precedes, lags, or is not related to
another time series. Specifically, this paper compares time series of
donations from clusters of political donors and times series of the
number of social media posts by each topic that were made by campaigns
that each donor cluster contributed to. For example, a time series of
donations from a donor cluster was compared to the aggregate count of
posts about a given topic made by candidates that the donor cluster
contributed to.

\hypertarget{results}{%
\section{Results}\label{results}}

Initial results suggest that both models of political donor
motivation--the access-oriented and consumptive models--are potentially
found. Different clusters of political donors exhibit different
behaviors. Some clusters of political donors show behavior that is
in-line with the access-oriented model, where their donations precede
public support of policy issues by the candidates that they contributed
to. Contribution from other donor clusters align with the conumptive
model of political donors and contributions from their cluster lag
public support of various policy issues by candidates. Other donor
clusters exhibit no behavioral connection to candidates' public support
of policy issues--suggesting that there is some confounding factor or
motivation for donating to the campaigns that they contributed to.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{wordcountaddin}\OperatorTok{:::}\KeywordTok{text_stats}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & koRpus & stringi\tabularnewline
\midrule
\endhead
Word count & 614 & 610\tabularnewline
Character count & 4017 & 4017\tabularnewline
Sentence count & 26 & Not available\tabularnewline
Reading time & 3.1 minutes & 3 minutes\tabularnewline
\bottomrule
\end{longtable}





\newpage
\singlespacing 
\end{document}
